---
title: "Data Jamboree- ggplot2"
output: html_document
---
###Import packages (once per machine)
```{r}
install.packages("readr", "ggplot2", "ggbeeswarm")
```

###Load packages (once per R session)
```{r}
library(readr)
library(ggplot2)
library(ggbeeswarm)
```

###Import data
We will be using a little bit of R to get started. We want to assign the data file to an R object using (<-). This imports our data and gives us the ability to call the data easily.
```{r}
heart <- read_csv("http://faculty.washington.edu/kenrice/heartgraphs/nhaneslarge.csv", na=".") #na= tells R that . is an na value
```

###Basic ggplot Anatomy
Let's start using ggplot2 to make some simple graphs. The code we use for ggplot is made of layers. It creates graphs by layering imformation on top of an empty graph.
```{r}
ggplot(heart, aes(x=DR1TFOLA)) 
#This says we want ggplot to use the data.frame heart and to plot DR1TFOLA on the x-axis.
```

We see that the command for ggplot does actually create a plot, but without any layers, it doesn't know how you want to plot your data.

Say that we want to make a histogram plot. We start with our ggplot command and add a geom layer by using the **+** sign.

```{r}
ggplot(heart, aes(x=DR1TFOLA)) +
  geom_histogram()
```

So same as before we said "ggplot, use the data.frame heart, make a plot with DR1TFOLA on the x-axis and now plot the frequency of DR1TFOLA by using a histogram type plot". What a good listener ggplot is!

Some of you may have been wondering what "DR1TFOLA" is. We find out by looking at the dataset that it means **folate intake**. Let's update the x-axis with this information so we know what we are looking at.

```{r}
ggplot(heart, aes(x=DR1TFOLA)) +
  geom_histogram() +
  labs(x = "Folate intake") #x-axis label
```

One of ggplot's great features is that you can customize your plot to look exactly the way you picture it in your head. We can start with changing some colors.

First, the outline of the bars by using colour in the geom_histogram layer.
```{r}
ggplot(heart, aes(x=DR1TFOLA)) +
  geom_histogram(colour = "white") + 
  labs(x = "Folate intake")
```

We can also change the fill of the bars by using fill in the geom_histogram layer. 
```{r}
ggplot(heart, aes(x=DR1TFOLA)) +
  geom_histogram(colour = "white", fill = "peachpuff") + #yes, that is a name of a color
  labs(x = "Folate intake")
```

Now, R has been bugging us about the binwidth of our histogram by telling us "## `stat_bin()` using `bins = 30`. Pick better value with `binwidth`."

```{r}
ggplot(heart, aes(x=DR1TFOLA)) + 
  geom_histogram(colour = "white", fill = "peachpuff", bins = 50)
```
